MINOS Handover Plots

### 2023-06-09 minos/validation/handovers.Rmd
Added spaghetti handover plots for all ordinal variables. Might seem a bit daft but they at least tell us that people are moving between the levels in each wave (and therefore can identify a major problem)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

@@

@@

@@

@@

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'housing_quality',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'loneliness',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.s <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nutrition_quality',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, phealth)
base.s <- base.dat %>%
  select(pidp, age, time, phealth)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'phealth',
               save = TRUE,
               save.path = save.path)

rm(raw.s, base.s, spag)
```
